Stock enhancement undermines ecological stability

### 2022-02-21 rmd/manuscript.Rmd
edit: title

---
title: "Stock enhancement undermines ecological community stability"
output:
  word_document:
    reference_docx: word_format.docx
csl: science.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: reference.bib
---

>>>>

---
title: "Stock enhancement undermines ecological stability"
output:
  word_document:
    reference_docx: word_format.docx
csl: science.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: reference.bib
---
